Boundary Conditions and Time Dependence of a Semi-Analytic Solution for Resonant Scattering

### 2022-03-29 ms.tex
Changing title and further adjusting time dependence motivation paragraph

\title{Resonant Scattering in a Uniform Sphere with Large Optical Depth}

\correspondingauthor{B. Connor McClellan}
\email{bcm2vn@virginia.edu}

@@

>>>>

\title{Boundary Conditions and Time Dependence of a Semi-Analytic Solution for Resonant Scattering}
% the paper formerly known as Resonant Scattering in a Uniform Sphere with Large Optical Depth
\correspondingauthor{B. Connor McClellan}
\email{bcm2vn@virginia.edu}

@@

\textbf{The motivation for including time-dependence in the transfer equation is to characterize the distribution of photon escape times, which is needed to calculate the energy deposited into the gas by an escaping photon. Additionally, steady-state solutions to this problem are not always sufficient to describe all the physics of \lya transport. Time-variable, optically-thick environments necessitate a time-dependent solution to include the dynamic effects of \lya transfer. These include the optical afterglow of gamma-ray bursts \citep{2010ApJ...716..604R} and \lya sources redshifted by cosmological expansion %, which may reveal information about their neutral hydrogen halos and the intergalactic medium 
\citep{2011MNRAS.418..853X}.}
